Floquet-Drude Conductivity in Dressed Quantum Hall Systems

### 2021-08-18 paper/v2.0/sections/6_manipulate_conductivity.tex
Correct figure numbers
Correct sec06

To identify the longitudinal conductivity characteristics of quantum Hall system under external dressing field, first we derive an expression for normalized longitudinal conductivity as a function of Fermi energy $X_F$ and intensity of the dressing field $I$.
Here we derive a normalized $x$-directional conductivity of dressed quantum Hall system using the natural conductivity of the least Landau level
\begin{equation} \label{eq:37}
  \begin{aligned}
    \widetilde{\sigma}^{xx} =
    \sigma_{0}
    \sum_{n} &
    \frac{(n+1)}{0.0037 \Lambda_n \Lambda_{n+1}} \\
    & \times
    \left[
      \frac{1}
      {
        1 + \left(\frac{X_F - n -1}{0.06\Lambda_n}\right)^2
      }
    \right]
    \left[
      \frac{1}
      {
        1 + \left(\frac{X_F - n}{0.06\Lambda_{n+1}}\right)^2
      }
    \right],
  \end{aligned}
\end{equation}
with $\sigma^0 = \flatfrac{e^2}{(\pi \hbar A)}$.

@@

\begin{figure}[t]
\includegraphics[scale=0.575]{figures/fig_5}
\caption{ Normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a  frequency of $\omega =\SI{2e12}{\radian\per\second}$ and $I_0 =\SI{100}{\watt\per\square\centi\metre}$. In this calculation, we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $\SI{0.24}{\milli\eV}$.}
\label{fig:5}
\end{figure}

\begin{figure}[t]
\includegraphics[scale=0.575]{figures/fig_6}
\caption{$3$rd Landau level’s normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a frequency of $\omega =\SI{2e12}{\radian\per\second}$ and $I_0 =\SI{100}{\watt\per\square\centi\metre}$.
In this calculation, we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $\SI{0.24}{\milli\eV}$}.
\label{fig:6}
\end{figure}

>>>>

To identify the longitudinal conductivity characteristics of quantum Hall system under external dressing field, first we derive an expression for normalized longitudinal conductivity as a function of Fermi energy $X_F$ and intensity of the dressing field $I$.
We can identifiy the normalized $x$-directional longitudinal conductivity of dressed quantum Hall system by
\begin{equation}\label{eq:37}
  \widetilde{\sigma}^{xx}(X_F,I) =
  \flatfrac{\sigma^{xx}}{\sigma_{0}},
\end{equation}
with $\sigma^0 = \flatfrac{e^2}{(\pi \hbar A)}$, and this can be expressed as
\begin{equation} \label{eq:38}
  \begin{aligned}
    \widetilde{\sigma}^{xx}(X_F,I) &=
    \sum_{n}
    \frac{(n+1)}{\alpha^2 \Lambda_n \Lambda_{n+1}} \\
    &\quad\times
    \left[
      \frac{1}
      {
        1 + \left(\frac{X_F - n -1}{\alpha \Lambda_n}\right)^2
      }
    \right]
    \left[
      \frac{1}
      {
        1 + \left(\frac{X_F - n}{\alpha \Lambda_{n+1}}\right)^2
      }
    \right],
  \end{aligned}
\end{equation}
where $\alpha = \flatfrac{\Gamma_0}{(2\hbar \omega_0)}$. Here, $\Gamma_0$ is the natural energy broadening of the least Landau level.

@@

\begin{figure}[t]
\includegraphics[scale=0.575]{figures/fig_4}
\caption{ Normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a  frequency of $\omega =\SI{2e12}{\radian\per\second}$ and $I_0 =\SI{100}{\watt\per\square\centi\metre}$. In this calculation, we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $\SI{0.24}{\milli\eV}$.}
\label{fig:5}
\end{figure}

\begin{figure}[t]
\includegraphics[scale=0.575]{figures/fig_5}
\caption{$3$rd Landau level’s normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a frequency of $\omega =\SI{2e12}{\radian\per\second}$ and $I_0 =\SI{100}{\watt\per\square\centi\metre}$.
In this calculation, we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $\SI{0.24}{\milli\eV}$.}
\label{fig:6}
\end{figure}
